Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
Additional simulation with different size of error, figure modification, add figure to the editor's comment

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
bibliography: ../ ML_VRA.bib
---

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. One of your comments was paritculary important and we were able to correct our mistake before this paper is published. So, thank you so much. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

@@

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly. Please also see the figure below. CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
</span>

>>>>

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
bibliography: ../ML_VRA.bib
---

```{r echo = F, include = FALSE, cache = F}
library(knitr)
library(here)
here::i_am("GitControlled/Writing/CEA_3rd_round/replies_rev.rmd")
# opts_knit$set(root.dir = here())

options(htmltools.dir.version = FALSE)
options(knitr.duplicate.label = "allow")

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = T,
  echo = F
)

library(data.table)
library(ggplot2)
```

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. One of your comments was particularity important and we were able to correct our mistake before this paper is published. So, thank you so much. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

@@

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly. Please also see the figure below. CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat. Please see the figure below showing some examples of yield response function estimated by CNN with "aabbyytt" modeling scenario. Each of the lines indicates yield response curve of a specific site.

```{r, fig.width=7, fig.cap = "An illustrative example of yield response functions estimated by CNN (scenario: aabbyytt)"}
cnn_simRes_temp <- readRDS(here("Shared/Results/ex_cnn_y_ResCurve.rmd"))

ggplot(cnn_simRes_temp, aes(x=rate, y=pred_yield, colour=factor(unique_subplot_id))) +
    geom_point(size = 0.7) +
    geom_smooth(method=lm, se=FALSE, size=0.3) +
    facet_wrap(~Model, ncol = 2) +
    theme(
        legend.title = element_blank(),
        legend.position = "none"
    ) +
  xlab("N (kg/ha)") +
  ylab("Predicted Yield (kg/ha)")
```

### 2022-03-18 Writing/appendix.rmd
Additional simulation with different size of error, figure modification, add figure to the editor's comment

## Appendix E: CNN performance per training epoch
The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration. For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.)

@@

## Appendix H: True Yields vs Predicted Yields by models

@@

>>>>

## Appendix E: CNN Performance per Training Epoch
The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration. For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.

@@

## Appendix H: True Yields vs Predicted Yields by Models

@@

## Appendix I: Simulations with Different Size of Yield Disturbance Term.
In this section, we present the results of EONR estimation and yield prediction with different size of yield disturbance term ($\varepsilon$). We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study. This can be done by just changing the variogram parameter of $psill$ for $\varepsilon$. $0.002$ of $psill$ value was used to create low $\varepsilon$, and $0.028$ of $psill$ value was used to create high $\varepsilon$. Figure I.1 illustrates examples of generated $\varepsilon$.

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure I.1: An example of experimental design of N and generated yield at the subplot resolution"}
field_m_error_low | field_m_error_high
```

Using those yield datasets, we conducted one hundred simulations. The results of EONR estimation and yield prediction are shown in Table XX. (what about CNN reuslts??)

```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
report_table_optN_low
```

```{r report-table-y-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
report_table_y_low
```

```{r report-table-optN-low, tab.cap = "Table I.3: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
report_table_optN_high
```

```{r report-table-y-low, tab.cap = "Table I.4: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
report_table_y_high
```
